\documentclass[10pt]{article}

% helpful packages
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}
\usepackage{hyperref}

% global formatting tweaks
\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}

% new commands!
\newcommand{\name}[1]{\begin{center}\section*{\huge #1}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.2cm}\section*{#1}\vspace{-0.2cm}\hrule\vspace{0.2cm}}



\begin{document}

\name{Matthew Yuan}
\topinfo{\href{https://github.com/code-by-matt}{github.com/code-by-matt}}
\topinfo{\href{mailto:my4@princeton.edu}{my4@princeton.edu}}
\topinfo{609-216-0038}

\resumesection{Education}

\textbf{Princeton University}, Princeton, NJ \hfill September 2017--May 2021 (Expected)
\begin{itemize}
	\item Bachelor of Arts (A.B.) in Mathematics, 3.8 GPA.
	\item Coursework includes Algorithms and Data Structures, Probability and Stochastic Systems, Computational Geometry, Linear Algebra, Multivariable Calculus, Combinatorics, Real Analysis, and Fourier Analysis.
\end{itemize}

\textbf{University of Oxford}, Oxford, UK (study abroad) \hfill January 2020--Present
\begin{itemize}
	\item One on-site trimester at Worcester College, one remote trimester.
	\item Coursework includes Artificial Intelligence (AI), Algebraic Number Theory, Topology, Philosophy of Mathematics.
\end{itemize}

\resumesection{Experience}

\textbf{Product Management Intern}, Roblox, Commerce Team \hfill May 2020--August 2020
\begin{itemize}
	\item Worked with engineering and design to gain insights about Roblox Premium subscribers. Product owner of a cancellation survey that received over 7000 responses within a week of launch.
	\item Presented to legal team an analysis of how competitors discourage friendly fraud, which informed new anti-friendly fraud features being planned for all Roblox users under 13.
	\item Contributed to strategic planning for new ad surfaces in the upcoming Roblox Universal App.
\end{itemize}

\textbf{Adversarial Machine Learning Researcher}, University of Oxford \hfill March 2020--Present
\begin{itemize}
	\item Study and implement existing attacks against deterministic neural networks.
	\item Propose and test new attacks against Bayesian neural networks, which are known to be more robust.
	\item Meet weekly (remotely) with a research assistant and a doctoral student to discuss progress.
\end{itemize}

\textbf{Course Assistant}, Princeton University \hfill September 2018--May 2019
\begin{itemize}
	\item Led weekly problem sessions for about 50 students in Real Analysis and Linear Algebra.
	\item Helped students understand complex mathematical ideas and guided students through homework problems.
\end{itemize}

\resumesection{Activities}

\textbf{Writer}, \href{https://medium.com/@my4}{medium.com/@my4} \hfill November 2018--Present
\begin{itemize}
	\item Write short stories on Medium about math, origami, and whatever else interests me in the moment.
	\item Articles featured by Medium on their Math and Design topic pages and published by Medium's largest active publication.
	\item Previously managed and wrote for a student-run publication that interviews startup founders.
\end{itemize}

\resumesection{Projects}

\textbf{Connect6 Bot} \hfill July 2020--Present
\begin{itemize}
	\item Program a bot that plays the abstract strategy game Connect6 using a combination of Monte-Carlo tree search (MCTS) and threat-space search. Written in Python.
	\item Bot will interface with the online game server Little Golem to play against hundreds of human Connect6 players.
\end{itemize}

\textbf{Author in Princeton Undergraduate Research Journal} \hfill Spring 2019
\begin{itemize}
	\item Presented a creative, narrative explanation of Carl Friedrich Gauss's discovery that the regular seventeen-sided polygon is constructible using a compass and straightedge.
	\item Driven by curiosity and a desire to understand the real-world historical context of Gauss's work.
	\item 1 of 5 papers selected for publication out of 23 total submissions.
\end{itemize}

\resumesection{Skills}

\textbf{Programming Languages and Technologies}
\begin{itemize}
	\item Python, Git, \LaTeX, JavaScript, HTML/CSS, Java.
\end{itemize}

\textbf{Concepts}
\begin{itemize}
	\item Product Management, Object-Oriented Programming, Machine Learning, Mathematical Reasoning, Teaching.
\end{itemize}

\textbf{Languages}
\begin{itemize}
	\item English, Mandarin.
\end{itemize}

\end{document}
