\documentclass[11pt]{article}

% helpful packages
\usepackage{geometry}
\usepackage{indentfirst}
\usepackage{enumitem}

% global formatting tweaks
\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{9pt}
\setlist{nosep}
\renewcommand\labelitemi{--}

% new commands!
\newcommand{\name}[1]{\begin{center}\section*{\huge #1}\end{center}}
\newcommand{\topinfo}[1]{\begin{center}\vspace{-0.2cm}#1\vspace{-0.2cm}\end{center}}
\newcommand{\resumesection}[1]{\vspace{-0.2cm}\section*{#1}\vspace{-0.2cm}\hrule\vspace{0.2cm}}



\begin{document}

\name{Matthew Yuan}
\topinfo{github.com/code-by-matt}
\topinfo{my4@princeton.edu}
\topinfo{609-216-0038}

\resumesection{Education}

\textbf{Princeton University}, Princeton, NJ \hfill September 2017--June 2021 (Expected)
\begin{itemize}
	\item Bachelor of Arts (A.B.) in Mathematics, 3.8 GPA.
	\item Coursework includes Macroeconomics, Algorithms and Data Structures, Probability and Stochastic Systems, Linear Algebra, Multivariable Calculus, Combinatorics, Real Analysis, and Fourier Analysis.
\end{itemize}

\textbf{Coursera}, coursera.org \hfill May 2019--Present
\begin{itemize}
	\item Machine Learning by Stanford University.
\end{itemize}

\resumesection{Experience}

\textbf{Algebraic Geometry Research}, Princeton University \hfill June 2019--Present
\begin{itemize}
	\item Study Shafarevich's \textit{Basic Algebraic Geometry 1} under Professor J\'{a}nos Koll\'{a}r.
	\item Meet weekly with Prof. Koll\'{a}r as part of a 7-person research group.
\end{itemize}

\textbf{Course Assistant}, Princeton University \hfill September 2018--Present
\begin{itemize}
	\item Lead weekly problem sessions for about 50 students in Real Analysis and Linear Algebra.
	\item Answer students' questions and guide students through homework problems.
\end{itemize}

\resumesection{Projects}

\textbf{Thue-Morse Connect Four}, github.com/code-by-matt/tmc4online  \hfill October 2018--Present
\begin{itemize}
	\item Built a variant of Connect Four where players take turns following the Thue-Morse sequence. Intended to eliminate the game's first-player advantage. See it at code-by-matt.github.io/connect4.
	\item Currently building a fully-featured version that will allow users to play each other online.
	\item Used HTML/CSS, JavaScript, Python, Django, PostgreSQL, Bootstrap, and Git.
\end{itemize}

\textbf{Seam Carving}, class project \hfill April 2019
\begin{itemize}
	\item Implemented an image resizing algorithm in Java that preserves the image's content without cropping or stretching.
	\item Achieved by using Dijkstra's algorithm to find minimal-energy seams in an image.
\end{itemize}

\resumesection{Activities}

\textbf{Author in Princeton Undergraduate Research Journal}, bit.ly/2W72vBR \hfill Spring 2019
\begin{itemize}
	\item Presented a creative, narrative explanation of Carl Friedrich Gauss's discovery that the regular seventeen-sided polygon is constructible using a compass and straightedge.
	\item Driven by curiosity and a desire to understand the real-world historical context of Gauss's work.
	\item 1 of 5 papers selected for publication out of 23 total submissions.
\end{itemize}

\textbf{Editor of Profiles in Entrepreneurship}, medium.com/profiles-in-entrepreneurship \hfill October 2018--Present
\begin{itemize}
	\item Manage a team of 4 writers for an intercollegiate publication that provides student entrepreneurs actionable advice from startup founders and VCs.
	\item Produced over 30 articles in the 2018--2019 school year.
\end{itemize}

\resumesection{Skills}

\textbf{Programming Languages and Frameworks}
\begin{itemize}
	\item Java, Python, HTML/CSS, JavaScript, Django, PostgreSQL, Bootstrap, Git, \LaTeX.
\end{itemize}

\textbf{Concepts}
\begin{itemize}
	\item Object-Oriented Programming, Machine Learning, Mathematical Reasoning, Teaching.
\end{itemize}

\textbf{Languages}
\begin{itemize}
	\item English, Mandarin.
\end{itemize}

\end{document}
